---
title: "Notes 486"
author: "Tracie-Lynn Lamoreux"
date: "2023-01-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
1. Introduction
2. Import
3. Tidy 
4. Transform (tidying and transforming is called wrangling) 

**Visualization**: Human activity, but do not scale well because they require a human to interpret. <br />
**Models**: Complimentary tools to visualization. <br />
**Communication**: Last step in data science. <br />
**Programming**: cross-cutting tool you use in every part of project. <br />



```{r, echo=FALSE}
library(tidyverse)
```
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```
<br />
* Each geom function in ggplot2 takes a mapping argument. <br />
1. Run ggplot(data=mpg). What do you see? <br />
```{r, echo = FALSE}
ggplot(data = mpg)
```
<br /> 2. How many rows are in mpg? How many columns? <br />
````{r, echo = FALSE}
dim(mpg)
```
<br /> 3. What does the drv variable describe? Read the help for ?mpg to find out. <br />
````{r, echo = FALSE}
?mpg
```
The type of drive train, where f = front-whell drive, r = rear wheel drive, 4 = 4wd.<br /> 
<br />
4. Make a scatterpolot of hwy vs cyl <br />
````{r, echo = FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = cyl, y = hwy))
```
<br /> 5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful? <br />
```{r, echo=FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```
<br />This plot is not useful because drv is nominal as well as the class variable.


# Aesthetic Mappings

